### 2021-04-13 conclusion.tex
More citations appeared :'(

Gay~\etal~\cite{gaynagarajan03} and Vasconcelos~\etal~\cite{vasconcelosravara04,vasconcelosgay06} were the first to introduce a functional language with session types. However, such works, including early GV~\cite{gayvasconcelos10,gayvasconcelos12} did not guarantee deadlock freedom, until it was addressed via syntactic restrictions~\cite{lindleymorris15,wadler14}. Toninho~\etal~\cite{toninhocaires12} present a translation of simply-typed $\lambda$-calculus into session-typed $\pi$-calculus. However, their focus is not on deadlock freedom.

>>>>

Gay~\etal~\cite{gaynagarajan03} and Vasconcelos~\etal~\cite{vasconcelosravara04,vasconcelosgay06} were the first to introduce a functional language with session types. However, such works, including early GV~\cite{gayvasconcelos12} did not guarantee deadlock freedom, until it was addressed via syntactic restrictions~\cite{lindleymorris15,wadler14}. Toninho~\etal~\cite{toninhocaires12} present a translation of simply-typed $\lambda$-calculus into session-typed $\pi$-calculus. However, their focus is not on deadlock freedom.
